Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
2.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

@@

## Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden. In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races. For example, Black individuals have a total vote of 5293 individuals for Biden, however only 642 individuals support and vote for Trump. This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals. Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters. The gender gap in voter turnout rates is the largest for Black voters. Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s. Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.

>>>>

1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
2.Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.

@@

## Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.

Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, and Asian individuals are more likely to vote and show support for Biden. In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races. For example, Hispanic individuals have a total vote of 2481 individuals for Biden, however only 1210 individuals support and vote for Trump. This same trend can also be observed in races such as Middle Eastern, Hispanic, and Asian individuals. Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters. The gender gap in voter turnout rates is the largest for Black voters. In @tbl-model-summary-tableLogistic of our paper, we observe a negative coefficient for black people (−1.030) in support for Biden, indicating that Black people are displaying less support and fewer votes for Biden. The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump. When the coefficient values are negative, which means the voters decrease their support in Biden. Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden. Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s. Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.
